Classifying Human Driving Behavior via Deep Neural Networks

### 2017-06-08 paper/paper-DrexelFormat.tex
Done
updated presentation

% ####################################################################################################################################
\chapter{Introduction}\label{chap:intro}
% ####################################################################################################################################
Most people spend several hours per day for driving vehicle when they go to work, school or shopping. Modern car systems collect real-time data of the car status and driving behavior of the driver. Moreover, such recorded data is a very promising data source for healthcare and research, which has currently been rarely been used. This paper is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia, George Mason University and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.

@@

Therefore,
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
= W_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= W_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$

>>>>

% ####################################################################################################################################
\chapter{Introduction}\label{chap:intro}
% ####################################################################################################################################
Most people spend several hours per day for driving vehicle when they go to work, school or shopping. Modern car systems collect real-time data of the car status and driving behavior of the driver. Moreover, such recorded data is a very promising data source for healthcare and research, which has currently rarely been used. This paper is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia, George Mason University and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.

@@

Therefore,
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$
